\huge Tor's Usability for Censorship Circumvention

### 2016-04-20 pets2017-paper/pets2017-paper.tex
qualitative section

Additionally, the progress bar has a bug
that causes it to draw itself only when the level of progress increases.
If progress bar reaches a certain level,
then the user closes the window,
the next time the progress bar appears it will apparenly have regressed to 0\%.
The apparent negative progress caused users to assume that their subsequent attempts were wrong, even if they were correct.

>>>>

Additionally, the progress bar has a bug
that causes it to draw itself only when the level of progress increases.
If progress bar reaches a certain level,
then the user closes the window,
the next time the progress bar appears it will apparently have regressed to 0\%.
The apparent negative progress caused users to assume that their subsequent attempts were wrong, even if they were correct.
